Flowers text analysis

### 2022-10-14 code/annotation_analysis.Rmd
work on helper funcs for game x end sim (not entirely working!)

---
title: "Flowers text analysis"
author: "vboyce"
output: html_document:
    toc: true
---

@@

make_within_df <- function(M_mat, F_mat, method) {
  M_mat %>%
    do(flatten_sim_matrix(get_sim_matrix(., F_mat, method = method),
                          .$repNum)) %>%
    mutate(rep1 = as.numeric(dim1), 
           rep2 = as.numeric(dim2)) 
}

@@

## Do groups diverge on labels?

@@

Wide variability -- some flowers might get more consistent names than others?

@@

```{r}
ggplot(player_similar, aes(x=quarter,y=sim,color=color))+
      stat_summary(aes(group=str_c(color,referent), color=color),fun.data = "mean_cl_boot", position = position_dodge(width=.3), alpha=.5, geom="point")+geom_smooth(formula=y~poly(x,2))
```

@@

```
This is really poorly labelled. Needs stats.

@@

@@

>>>>

---
title: "Flowers text analysis"
author: "vboyce"
output:
  html_document:
    toc: true
    toc_depth: 2
---

@@

@@

### TODO model
## Do groups diverge on labels?

@@

Wide variability -- some flowers might get more consistent names than others?
### TODO model

@@

```{r}
ggplot(player_similar, aes(x=quarter,y=sim,color=color))+
      stat_summary(aes(group=str_c(color,referent), color=color),fun.data = "mean_cl_boot", position = position_dodge(width=.3), alpha=.5, geom="point")+geom_smooth(formula=y~poly(x,2))
```
### TODO model

@@

```
This is really poorly labelled. Needs stats. 
### TODO models

@@

```
### TODO models

d.raw_chat <- read_csv(here(paste(read_data_path, 
                                  "raw_chat.csv", 
                                  sep="")),
                      col_types = cols()) %>% distinct() |> 
  select(gameId, playerId) |> unique()

d.players <- read_csv(here(paste(read_data_path, "players.csv", sep = "")),
                      col_types = cols()) %>% distinct() |> select(playerId,name) |> inner_join(d.raw_chat)

sbert_single <- read_csv(here(annotation_path,"pre_sbert.csv")) %>% bind_cols(readRDS(here(annotation_path,'post_sbert.RData')))  %>% as_tibble() |> 
   left_join(d.players)
```

```{r to-end-helpers}

#here we only want sims between an in-game utt and an end description
# note: cor expects features to be in columns so we transpose

pairwiseCosine <- function(matrix1,matrix2) {
    apply(matrix1,2,function(x){
        apply(matrix2,2,lsa::cosine,x)
    })
}
get_sim_matrix = function(df, F_mat, method = 'cosine') {
  df_game <- df |> filter(type=="game")
  df_end <- df |> filter(type=="end")
  feats_game = F_mat[df_game$feature_ind,]
  print(t(feats_game))
  feats_end = F_mat[df_end$feature_ind,]
  print(t(feats_end))
  if(method == 'cor') {
    return(cor(t(feats_game), t(feats_end), method = 'pearson'))
  }  else if (method == 'cosine') {
    return(as.matrix(pairwiseCosine(t(feats_game), t(feats_end))))
  } else {
    stop(paste0('unknown method', method))
  }
}

# note this does de-duplicated version
flatten_sim_matrix <- function(cormat, ids_game, ids_end) {
  data.frame(
    dim1 = ids_end[row(cormat)],
    dim2 = ids_game[col(cormat)],
    sim  = as.numeric(cormat)
  ) %>%
    mutate(dim1 = as.character(dim1),
           dim2 = as.character(dim2))
}

make_across_df <- function(M_mat, F_mat, method) {
  M_mat %>%
    do(flatten_sim_matrix(get_sim_matrix(., F_mat, method = method),
                          as.character(filter(., type=="game")$combinedId), as.character(filter(., type=="end")$combinedId)))
}

@@

** Does not work with grouped data frames, works with non-grouped dfs ** 
```{r}
#test
test_df1 <- tibble(color=c("blue","green"),id=c("game1","game2"), val1=c(.5,.7), val2=c(.9,.4)) |> mutate(type="game")
test_df2 <- tibble(color=c("blue", "green"),id=c("end1", "end2"), val1=c(1,-1), val2=c(-1,-1)) |> mutate(type="end")
test <- test_df1 |> union(test_df2) 
F_mat <- test %>% select(starts_with("val")) %>% as.matrix() #Features
M_mat <- test%>% select(-starts_with("val")) %>% mutate(feature_ind=row_number(), combinedId=id) |> group_by(color)

a <- make_across_df(M_mat, F_mat, method="cosine")

# want there to be one thing that gets grouped (M_mat) and then we separate it by type

sol <- tibble(dim1=c("end1","end2","end1","end2"), 
              dim2=c("game1", "game1", "game2","game2"),
              sim=c(lsa::cosine(c(.5,.9),c(1,-1)),
                    lsa::cosine(c(.5, .9), c(-1,-1)),
                    lsa::cosine(c(.7,.4),c(1,-1)),
                    lsa::cosine(c(.7,.4),c(-1,-1))))
```

# TODO: Correlates of success

# TODO: scale of variation between groups
